On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2024-01-08 Manuscript/reply.tex
Fixed pdf compile
quick comments

Thank you for this suggestion. The motivation behind the proposed
recentered CI is that. for the autocorrelation parameter in the
simulation studies, the centers of the existing CIs appeared to be a
biased estimator of the target while the spreadness of the CIs still
provide good uncertainty measures. This has now been added in the
Recentered Percentile CI pargarph.

@@

\jy{Could you put the three plots in one? Perhaps use facet grid: phi
  by parameter (mu, sigma, phi). Then we just need one caption.}
\mc{I think it looks good, only problem is I'm not sure how friendly it is for
colorblind people. I used a palette which is supposed to be more colorblind
friendly}

@@

%We find that this format
%is a little
%cluttered to make comparisons, so we have elected to remain with the original 
%format.

@@

You are correct. To remedy this, the text highlighting the simulation study with 
an exponential marginal 
distribution from the Appendix has been moved to the Simulation Study 
section.

@@

\jy{Are there big differences? We could report the CP CIs in the paper.}
\mc{I included it in the paper but they do not seem too different}

@@

%CIs for $\mu$ exhibit coverage rates quite close to 1 for $\phi = -0.4$, and
%as stated before, the Wald-type CI is known to have undercoverage in such 
%situations.
%Figure~\ref{fig:norm_mu_1_cp} shows the same coverage rates using exact 
%Clopper-Pearson intervals to verify that it is the choice of Wald interval
%does not cause undercoverage of the coverage rate. Indeed, the widths of the
%exact proportion CIs do not seem to differ heavily from the Wald-type CIs.

@@

Thank you for the suggestion. However, because of the deterioration for $\phi$, 
we found it hard to fix the limits on the 
y-axis without hurting the visualization for the other rows. 
Figure~\ref{fig:alt_phi1} is provided as an example:

@@

\jy{I'm interested in seeing the figures overlaid as in
  Figure~\ref{fig:mu}.}
\mc{addressed}\jy{Put them overlaid; three plots in one with facet
  grid as the last one.}
  \mc{addressed. I think the last one looks better}

>>>>

Thank you for this suggestion. The motivation behind the proposed
recentered CI is that. for the autocorrelation parameter in the
simulation studies, the centers of the existing CIs appeared to be a
biased estimator of the target while the spreads of the CIs still
provide good uncertainty measures. This has now been added in the
Recentered Percentile CI paragraph.

@@

\jy{Lets use the new graph in the paper too. You may also use
  different line types to distinguish them.}

\jy{Use latex symbols for mu, sigma, phi in the plots.}

@@

@@

Agreed. The text highlighting the simulation study with an exponential marginal
distribution from the Appendix has been moved to the Simulation Study 
section.

@@

\jy{Are there big differences? We could report the CP CIs in the paper.}
\mc{I included it in the paper but they do not seem too different}
\jy{Point out the location of the changes in the text.}

@@

@@

Thank you for the suggestion. However, because of the deterioration for $\phi$, 
we found it hard to fix the limits on the 
y-axis without hurting the visualization for the other rows. 
Figure~\ref{fig:alt2_norm1} is provided as an example:

@@

%\jy{I'm interested in seeing the figures overlaid as in
%  Figure~\ref{fig:mu}.}
\mc{addressed}\jy{Put them overlaid; three plots in one with facet
  grid as the last one.}
  \mc{addressed. I think the last one looks better}
